Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with Uniform Kernels

### 2016-02-28 main_paper.tex
Correct several misspellings in the paper

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology, among
others. This strategy exploits the fact that many programs use somewhat
arbitrary threshoolds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.

@@

This section provides additional details of RD estimators in general and of
CCT's proposed bias correction. It also defines some of the notation and
presents the assumptions that will be used for our theoretical anaysis in
Section~\ref{boot}.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accomodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design. We focus on the linear case for ease in
  exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator
of $\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
\end{align*}

@@

Table \ref{Tb: simulation 1} presents the results for the local linear model, with three panels reporting on each DGP described above. For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and lenght for the four methods. For the three DGPs coverage for
    both analytical and bootstrap based bias correction methods is near nominal size but with slight undercoverage for CCT's analytical correction. For DGP 1, our robust bootstrap method improves coverage slightly, obtaining 93.1\% coverage against 92.4\% from CCT's analytical correction using the uniform kernel. Also, the CI length is slightly shortened on average. Both robust approaches improve over the naive estimator, even in this case for which bias is relatively small.

For the second DGP, based on \cite{ludwig2007}, the importance of correcting for the leading bias term presence becomes clear, with the naive bootstrap CI displaying an empirical coverage of only 86.9\%. Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and lenght from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.

@@

We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}. Bias-corrected point estimates and robust confidence intervals are reported. For completeness, we also include results following the procedure proposed by CCT. In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper. Instead, we used uniform kernel and obtained exactely the same results as theirs.}. The procedure proposed by CCT provides analytical standard error and confidence interval. Our bootstrap procedure provides standard error and confidence interval from the bootstrap distribution. In both CCT and bootstrap procedures, we set $p = 1$, $q = 2$ and used uniform kernel. In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.

@@

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
\begin{align*}
  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*_h - \E^*\hat\tau^*_h
   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitons as
$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
substitiutions of ``$-$'' for ``$+$.''

@@

>>>>

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology, among
others. This strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.

@@

This section provides additional details of RD estimators in general and of
CCT's proposed bias correction. It also defines some of the notation and
presents the assumptions that will be used for our theoretical analysis in
Section~\ref{boot}.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design. We focus on the linear case for ease in
  exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator
of $\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
\end{align*}

@@

Table \ref{Tb: simulation 1} presents the results for the local linear model, with three panels reporting on each DGP described above. For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and length for the four methods. For the three DGPs coverage for
    both analytical and bootstrap based bias correction methods is near nominal size but with slight undercoverage for CCT's analytical correction. For DGP 1, our robust bootstrap method improves coverage slightly, obtaining 93.1\% coverage against 92.4\% from CCT's analytical correction using the uniform kernel. Also, the CI length is slightly shortened on average. Both robust approaches improve over the naive estimator, even in this case for which bias is relatively small.

For the second DGP, based on \cite{ludwig2007}, the importance of correcting for the leading bias term presence becomes clear, with the naive bootstrap CI displaying an empirical coverage of only 86.9\%. Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and length from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.

@@

We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}. Bias-corrected point estimates and robust confidence intervals are reported. For completeness, we also include results following the procedure proposed by CCT. In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper. Instead, we used uniform kernel and obtained exactly the same results as theirs.}. The procedure proposed by CCT provides analytical standard error and confidence interval. Our bootstrap procedure provides standard error and confidence interval from the bootstrap distribution. In both CCT and bootstrap procedures, we set $p = 1$, $q = 2$ and used uniform kernel. In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.

@@

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
\begin{align*}
  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*_h - \E^*\hat\tau^*_h
   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
substitutions of ``$-$'' for ``$+$.''

@@

%  LocalWords:  Calonico Cattaneo Titiunik's Econometrica CCT AMSE CCT's DGP
%  LocalWords:  datasets frolich calonico HTV CIs
